Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-04 krs-survey.tex
Added an abstract
While here:
- changed the title to emphasis the 'requirements of KRS' aspect

\title{Current State of Knowledge Representation Systems for Robotics}
\author{Séverin Lemaignan, Moritz Tenorth, Michael Beetz}

@@

>>>>

\title{Requirements and Current State of Knowledge Representation Systems for Service Robotics}
\author{Séverin Lemaignan, Moritz Tenorth, Michael Beetz}

@@

\begin{abstract}

The aim of this contribution is two-fold: we first propose a typology of
knowledge representation systems for service robotics that covers intrinsic
features like expressiveness or reasoning techniques as well as extrinsic
features like knowledge acquisition and integration into pre-existent robotic
architectures.

We then survey the current knowledge representation system in the community to
identify which knowledge-bound cognitive abilities are today well understood
and implemented, and which would require more efforts.

We hope this article may bring a clearer picture of the challenges of knowledge
representation and manipulation for the robotics research community.

\end{abstract}
